---
title: "My R Markdown Primer"
author: "Yasmine Graham"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

R Markdown is a tool that allows you to combine text, code, and output in one document. It helps make analysis reproducible and easy to share.

## Narrative Example

This is a paragraph written in Markdown. You can use **bold**, *italics*, and lists:

-Easy to use
-Combines code and text
-Great for reports

## Math Example (LaTeX)

Inline math: $\alpha + \beta = \gamma$

Displayed math:

$$
E = mc^2
$$

```{r}

data(mtcars)
summary(mtcars)

```

##Plots example

You can also embed plots, for example:

```{r}

library(ggplot2)

ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point()
```

## Reflection: Using R Markdown was helpful because it combines writing and coding in one place. It makes reports more efficient since results update automatically. One challenge I faced was understanding when to use code chunks versus regular text, but it became clearer with good practice.
